Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-11-30 journal paper/content/sec-intro.tex
add updated poster and edits in journal sec

Given the prevalence of these technologies and the increased importance of data in the digital economy, our main high-level question is: {\bf does competition lead to the adoption of better exploration algorithms?} This translates into a number of more concrete questions. While it is commonly assumed that ``better" technology always helps, is this so for our setting? Does increasing competition lead to higher consumer welfare? To what extent is there a ``data feedback loop" where one firm having more data leads to that firm attracting more users which leads to that firm having more data, etc.?

>>>>

Given the prevalence of these technologies in the digital economy, our main high-level question is: {\bf does competition lead to the adoption of better exploration algorithms?} This translates into a number of more concrete questions. While it is commonly assumed that ``better" technology always helps, is this so for our setting? Does increasing competition lead to higher consumer welfare? To what extent is there a ``data feedback loop" where one firm having more data leads to that firm attracting more users which leads to that firm having more data, etc.?
